Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
small section 2 reformulation

\begin{theorem}
  Let $\mu$ be an ordinal strictly less than $\epsilon_0$.
  There is no function mapping hydras to the segment $[0,\mu)$ that could be a measure used in proving the termination of  \emph{any} hydra battle.\label{thm3}
\end{theorem}

>>>>

\begin{theorem}
  Let $\mu$ be any ordinal strictly less than $\epsilon_0$.
  There is no function mapping hydras to the segment $[0,\mu)$ that could be used as a measure in proving termination for \emph{any} hydra battle.\label{thm3}
\end{theorem}
